---
title: "Kaggle Survey 2018 - The Girl Power"
output:
  html_document:
    number_sections: false
    fig_caption: true
    toc: true
    fig_width: 8
    fig_height: 6
    theme: united
    highlight: zenburn
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### What have we got here?

The dataset we have got here is a survey dataset that's filled by members of Kaggle Community. This dataset has very well captured many information about the mindset of Kagglers. 


### What can we do with it?


This Kernel aims to mine Kaggle Survey 2018 Dataset with a Girl Power lens where Female respondents are the primary focus, hoping the insights from it could help drive Female inclusion in the community. 


### Libraries

```{r, message = FALSE, warning=FALSE}
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(highcharter))
```


```{r, message = FALSE, warning=FALSE}
survey <- read_csv("input/multipleChoiceResponses.csv", skip = 1, col_types = cols())
```

### Filtering  entries marked by respondents mentioning Gender as Female 

While there could be many different entries made under Gender, we will consider only `Female` and `Male` (for comparison) in our further Analysis. 

```{r}
female <- survey %>% filter(`What is your gender? - Selected Choice` %in% "Female") %>% 
  rename("Gender" = `What is your gender? - Selected Choice`)

male <- survey %>% filter(`What is your gender? - Selected Choice` %in% "Male") %>% 
  rename("Gender" = `What is your gender? - Selected Choice`)


mf <- rbind(female,male)
```


### What's the age range of Female respondents?

Let us begin with a simple understanding of the age range of the Female respondents. 

```{r}
mf %>% group_by(Gender) %>% count(`What is your age (# years)?`) %>% 
   mutate(n = round((n/ sum(n)) * 100)) %>% 
  rename( "Age" = `What is your age (# years)?`) %>% 
  hchart("column",hcaes(x = "Age", y = "n", group = "Gender")) %>% 
  hc_title(text = "Female vs Male - Age Distribution %") %>% 
hc_add_theme(hc_theme_darkunica()) %>% 
    hc_xAxis(title = list(text = "Gender")) %>% 
    hc_yAxis(title = list(text = "Percentage of Respondents"),labels = list(format = "{value}%"))

  
```



### Country where are you from?

The place where we come from plays a vital role in becoming what we are. The next obvious thing to look into the details of our Female Kagglers is their Place of Residence. 

```{r}
mf %>% group_by(Gender) %>% count(`In which country do you currently reside?`) %>%
  
  mutate(n = round((n/ sum(n)) * 100)) %>% 
  rename( "Country" = `In which country do you currently reside?` ) %>% 
   
  
  hchart("column",hcaes(x = "Country", y = "n", group = "Gender")) %>% 
  hc_title(text = "Female vs Male - Age Distribution %") %>% 
hc_add_theme(hc_theme_darkunica()) %>% 
    hc_xAxis(title = list(text = "Gender")) %>% 
    hc_yAxis(title = list(text = "Percentage of Respondents"),labels = list(format = "{value}%"))

  
```
 


### Annual Salary


```{r}


mf %>% group_by(Gender) %>% count(`What is your current yearly compensation (approximate $USD)?`) %>%
  rename( "Salary" = `What is your current yearly compensation (approximate $USD)?` ) %>% 
  filter(! Salary %in% 18) %>% 
  mutate(n = round((n/ sum(n)) * 100, 3)) %>% 
  
  hchart("column",hcaes(x = "Salary", y = "n", group = "Gender")) %>% 
  hc_title(text = "Female vs Male - Salary Distribution %") %>% 
  hc_add_theme(hc_theme_darkunica()) %>% 
    hc_xAxis(title = list(text = "Gender")) %>% 
    hc_yAxis(title = list(text = "Percentage of Respondents"),labels = list(format = "{value}%"))

 
```


```{r}
male %>% count(`In which country do you currently reside?`) %>%
  rename( "Country" = `In which country do you currently reside?` ) %>% 
  hchart("column",hcaes("Country","n")) %>% 
  hc_title(text = "male - Country of Residence ") %>% 
  hc_add_theme(hc_theme_darkunica()) 
```




### Programming Language Choice

```{r}

female %>% count(`What specific programming language do you use most often? - Selected Choice`) %>%
  rename( "Language" = `What specific programming language do you use most often? - Selected Choice`) %>% 
  hchart("column",hcaes("Language","n")) %>% 
  hc_title(text = "Female - Programming Language used most often") %>% 
  hc_add_theme(hc_theme_darkunica())

```

```{r}

male %>% count(`What specific programming language do you use most often? - Selected Choice`) %>%
  rename( "Language" = `What specific programming language do you use most often? - Selected Choice`) %>% 
  hchart("column",hcaes("Language","n")) %>% 
  hc_title(text = "Male - Programming Language used most often") %>% 
  hc_add_theme(hc_theme_darkunica()) 

```




### WIP

This quick Kernel without any proper nararation is to tell myself that "Hey you've started something, Go do it!". I'll update this Kernel regularly. Please share your suggestions to improve or what insights to see!